Illustrative trajectories

### 2025-01-12 R/simulation_study_CRCVM/CRCVM_examples/illustrative_trajectories.Rmd
fix measurement error in simulation study

ftau_gaussian_fjords=function(cov_data) {
  ftau_gaussian(cov_data,sigma_bump=0.4,sigma_dip=0.4,tau0=1,dtau_bump=1.5,dtau_dip=0.5
                )
  }

@@

@@

@@

x.min= min(c(data_sim_fjords_cubic_repulsive_sub$y1,data_sim_fjords_cubic_attractive_sub$y1,
             data_sim_fjords_hanks_sub$y1))-1
x.max = max(c(data_sim_fjords_cubic_repulsive_sub$y1,data_sim_fjords_cubic_attractive_sub$y1,
              data_sim_fjords_hanks_sub$y1))+1
y.min = min(c(data_sim_fjords_cubic_repulsive_sub$y2,data_sim_fjords_cubic_attractive_sub$y2,
              data_sim_fjords_hanks_sub$y2))-1
y.max = max(c(data_sim_fjords_cubic_repulsive_sub$y2,data_sim_fjords_cubic_attractive_sub$y2,
              data_sim_fjords_hanks_sub$y2))+1

@@

  ggplot() +
    geom_sf(data = geometries %>% filter(domain == !!domain), aes(geometry = geometry), fill = "grey", inherit.aes = FALSE) +
    coord_sf(datum = st_crs("+init=EPSG:32626 +units=km")) +
    geom_path(data = data_filtered, aes(x = y1, y = y2, col = ID), size = 0.1) +
    geom_point(data = data_filtered, aes(x = y1, y = y2, col = ID), size = 0.1) +
    geom_point(data = x0, aes(x = x1, y = x2), shape = 3, size = 2, col = "red") +
    theme_minimal() +
    xlab("x") + ylab("y") +
    theme(legend.position = "none")  # Remove legend from individual plots
}

@@

>>>>

@@

```{r simulate hanks reflected in rectangle,cache=TRUE}
# Generate samples ---------------
cores=detectCores()
cl <- makeCluster(6) #not to overload your computer
registerDoParallel(cl)

@@

#stop cluster
stopCluster(cl)
```

```{r simulate hanks reflected in rectangle,cache=TRUE}
```

@@

x.min= min(c(data_sim_fjords_cubic_attractive_sub$y1,
             data_sim_fjords_hanks_sub$y1))-1
x.max = max(c(data_sim_fjords_cubic_attractive_sub$y1,
              data_sim_fjords_hanks_sub$y1))+1
y.min = min(c(data_sim_fjords_cubic_attractive_sub$y2,
              data_sim_fjords_hanks_sub$y2))-1
y.max = max(c(data_sim_fjords_cubic_attractive_sub$y2,
              data_sim_fjords_hanks_sub$y2))+1

@@

  ggplot() +
    geom_sf(data = geometries %>% filter(domain == !!domain), aes(geometry = geometry), fill = "grey", inherit.aes = FALSE) +
    coord_sf(datum = st_crs("+init=EPSG:32626 +units=km")) +
    geom_path(data = data_filtered, aes(x = y1, y = y2, col = ID), size = 0.1) +
    geom_point(data = data_filtered, aes(x = y1, y = y2, col = ID), size = 0.1) +
    geom_point(data = x0, aes(x = x1, y = x2), shape = 3, size = 2, col = "red") +
    theme_minimal() +
    xlab("x") + ylab("y") +
    theme(legend.position = "none") +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 16),
    axis.title.y = element_text(angle = 0)  # Rotate the y-axis label and adjust horizontal justification
  )
}

@@

#plot only trajectory in fjords

data_combined_fjords=data_combined[data_combined$domain=="Fjords",]

# Create a list of plots
plot_list <- lapply(seq_len(length(unique(data_combined$model))), function(i) {
  model <- unique_combinations$model[i]
  create_plot(domain="Fjords",model)
})

final_plot_fjords=ggarrange(plotlist=plot_list,
                     ncol=1, nrow=2, common.legend = TRUE, legend="bottom",
                     labels= c("shore-attractive CVM","shore-reflected CVM"))

final_plot_fjords

ggsave("illustrative_trajectories_fjords.pdf", plot = final_plot_fjords, width = 14, height = 14)
